---
title: "Figure_ext6_bacChoice"
author: "Mike O'Donnell"
date: "6/19/2018"
output: 
  html_document:
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = FALSE)
library(ProvidenciaChemo)
library(rstanarm)
library(tidybayes)
library(modelr)
library(tidyverse)
library(emmeans)
```

```{r food data input}
library(rstanarm)
library(tidybayes)
library(modelr)

choice <- read_csv(here::here("extdata/Figure_4E_2KOchoice.csv")) %>%
  mutate(food = fct_relevel(food, c("OP50","JUb39")),
         N_total = N_OP50 + N_Test,
    index = (N_Test - N_OP50) / N_total, 
    plateID = factor(seq(1:nrow(.))),
    p = N_Test / N_total,
    logit_p = boot::logit(p),
    strain = food,
    data_type = "raw")
```

```{r food choice data input}
library(rstanarm)
library(tidybayes)
library(modelr)


#singular fit#
glmm_mod1 <- lme4::glmer(data = choice %>%
                           mutate(strain = fct_relevel(strain, "JUb39")),
                         cbind(N_Test, N_OP50) ~ strain + (1|date) + (1|plateID), family = binomial) #%>%

glmm_mod2 <- lme4::glmer(data = choice %>% 
                           mutate(strain = fct_relevel(strain, "JUb39")),
                         cbind(N_Test, N_OP50) ~ strain + (1|plateID), family = binomial) #%>%

glmm_mod2 %>% emmeans(~strain) %>% emmeans::contrast(method = "pairwise")

#------------bayesian mod for experiment 1------------
stan_mod <- rstanarm::stan_glmer(data = choice %>%
                                   mutate(strain = fct_relevel(strain, "JUb39")),
                     cbind(N_Test, N_OP50) ~ strain + (1|plateID) + (strain|date),
                     family = binomial,
                     cores = 6,
                     chains = 4,
                     adapt_delta = 0.99)

fitted <- choice %>%
  data_grid(strain, test_bac) %>%
  add_fitted_draws(stan_mod, re_formula = NA) %>%
  mutate(logit_p = boot::logit(.value), data_type = "fit")

fitted1 <- emmeans(stan_mod, pairwise ~ strain)$contrasts %>% 
  #emmeans(stan_mod2,  ~ (strain | genotype)) %>%
  coda::as.mcmc() %>% 
  bayesplot::mcmc_intervals_data(prob = 0.66, prob_outer = 0.95) %>%
  mutate(
         data_type = "fit",
         strain = c("JUb39", "JUb39; tdcDel::cmR delAADC", "NA")) %>%
  filter(!strain == "NA") %>%
  mutate(strain = fct_relevel(strain, "JUb39")) %>% 
  mutate_if(is.numeric, funs(. * -1))


```

```{r}
#-------------barplot - non-normalized-----
# plot <- choice %>%
#     filter(genotype == "N2",
#            !date %in% c("2019_10_19", "2019_10_22", "2019_11_5", "2019_11_6", "2019_11_8", "2019_11_13")) %>%
#     ggplot(aes(x = data_type, y = logit_p)) +
#     geom_bardots(fillvar = strain, dotvar = strain) +
#     facet_grid(. ~ strain) +
#     scale_x_discrete(labels = function(strain) str_wrap(strain, width = 10)) +
#     labs(y = "Test bacteria preference (log-odds)") +
#   guides(colour = FALSE) +
#   scale_color_plot(palette = "grey-blue-green", drop = TRUE) +
#     scale_fill_plot(palette = "grey-blue-green", drop = TRUE) +
#     stat_pointinterval(aes(y=logit_p, x = 1.4),
#                        data = fitted, fatten_point = 0,
#                        size_range = c(0.3, 1), colour = "grey") +
#     stat_summary(data = fitted,
#                  aes(y=logit_p, x = 1.4),
#                  fun.y = median,
#                  fun.ymin = median,
#                  fun.ymax = median,
#                  geom = "crossbar",
#                  width = 0.05,
#                  alpha = 0.75,
#                  lwd = 0.35,
#                  colour = "darkgrey") +
#     guides(fill = FALSE) +
#     #figure.axes() +
#     add.n(data_type)
# 
# plot




#generate relative index values:
means <- choice %>%
      filter(strain == "OP50") %>%
      #group_by(date) %>%
      summarise(meanOP50 = median(logit_p))

#choice <- full_join(choice, means) %>% mutate(rel.Logit = logit_p - meanOP50) %>% droplevels()
choice <- choice %>%
  mutate(rel.Logit = logit_p - means$meanOP50)


plot1 <- choice %>%
  droplevels() %>%
  ggplot(aes(x = data_type)) +
  geom_hline(yintercept = 0, lty = 2, alpha = 0.2) +
  geom_boxplot(aes(fill = strain, y = rel.Logit), outlier.shape = NA, alpha = 0.75) +
  ggbeeswarm::geom_quasirandom(aes(colour =  strain, y = rel.Logit), width = 0.1, alpha = 0.5) +
  facet_grid(. ~ strain) +
  scale_x_discrete(labels = function(strain) str_wrap(strain, width = 10)) +
  labs(y = "Relative JUb39 preference (log-odds ratio)") +
  guides(colour = FALSE) +
  scale_color_plot(palette = "grey-blue-light", drop = TRUE) +
  scale_fill_plot(palette = "grey-blue-light", drop = TRUE) +
  # stat_pointinterval(aes(y = logit_p, x = 1.4),
  #   data = fitted, fatten_point = 0,
  #   size_range = c(0.3, 1), colour = "grey"
  # ) +
  # stat_summary(
  #   data = fitted,
  #   aes(y = logit_p, x = 1.4),
  #   fun.y = median,
  #   fun.ymin = median,
  #   fun.ymax = median,
  #   geom = "crossbar",
  #   width = 0.05,
  #   alpha = 0.75,
  #   lwd = 0.35,
  #   colour = "darkgrey"
  #  ) +
  geom_linerange(
    data = fitted1,
    aes(
      x = 1.5,
      ymin = ll,
      ymax = hh
    ),
    lwd = 0.35,
    colour = "grey34"
  ) +
  geom_crossbar(
    data = fitted1,
    aes(
      y = m,
      x = 1.5,
      ymin = l,
      ymax = h
    ),
    width = 0.05,
    lwd = 0.35,
    alpha = 0.5,
    colour = "grey69",
    fill = "grey69"
  ) +
  guides(fill = FALSE) +
  # figure.axes() +
  coord_cartesian(ylim = c(-2, 1.5)) +
  add.n(data_type)


#move down#
stan_mod %>% emmeans::emmeans(~ strain) %>% emmeans::contrast(method = "pairwise") %>%
  coda::as.mcmc() %>% bayesplot::mcmc_intervals()


glmm_mod2 %>% emmeans::emmeans(~ strain) %>% emmeans::contrast("trt.vs.ctrl")


```{r}
#second plot for tbh-1, octr-1

#generate relative index values:
means <- choice %>%
      filter(strain == "OP50",
             N_total > 10,
             is.na(note)) %>%
      group_by(genotype, date) %>%
      summarise(meanOP50 = mean(logit_p))

choice <- full_join(choice, means) %>% mutate(rel.Logit = logit_p - meanOP50) %>% droplevels()


plot1 <- choice %>%
  droplevels() %>%
  ggplot(aes(x = data_type)) +
  geom_hline(yintercept = 0, lty = 2, alpha = 0.2) +
  geom_boxplot(aes(fill = strain, y = rel.Logit), outlier.shape = NA, alpha = 0.75) +
  ggbeeswarm::geom_quasirandom(aes(colour =  strain, y = rel.Logit), width = 0.1, alpha = 0.5) +
  facet_grid(. ~ genotype + strain) +
  scale_x_discrete(labels = function(strain) str_wrap(strain, width = 10)) +
  labs(y = "Relative JUb39 preference (log-odds ratio)") +
  guides(colour = FALSE) +
  scale_color_plot(palette = "grey-blue", drop = TRUE) +
  scale_fill_plot(palette = "grey-blue", drop = TRUE) +
  # stat_pointinterval(aes(y = logit_p, x = 1.4),
  #   data = fitted, fatten_point = 0,
  #   size_range = c(0.3, 1), colour = "grey"
  # ) +
  # stat_summary(
  #   data = fitted,
  #   aes(y = logit_p, x = 1.4),
  #   fun.y = median,
  #   fun.ymin = median,
  #   fun.ymax = median,
  #   geom = "crossbar",
  #   width = 0.05,
  #   alpha = 0.75,
  #   lwd = 0.35,
  #   colour = "darkgrey"
  #  ) +
  geom_linerange(
    data = fitted1,
    aes(
      x = 1.5,
      ymin = ll,
      ymax = hh
    ),
    lwd = 0.35,
    colour = "grey34"
  ) +
  geom_crossbar(
    data = fitted1,
    aes(
      y = m,
      x = 1.5,
      ymin = l,
      ymax = h
    ),
    width = 0.05,
    lwd = 0.35,
    alpha = 0.5,
    colour = "grey69",
    fill = "grey69"
  ) +
  guides(fill = FALSE) #+
  # figure.axes() +
  #coord_cartesian(ylim = c(-.5, 1)) +
  #add.n(data_type)

space_facets(plot1, n_facets = 3, major_div = 2)

```
